---
title: "R Project 1 - Hello R"
author: "Junhao Feng"
date: "Due Fed 3rd"
output: html_document
---

## Link to my GitHub repository:
### https://github.com/fengj2/Data2401_RProj1
### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```
```{r datasaurus_dozen}
datasaurus_dozen %>%
  count (dataset) %>%
  print (13)
```


### Exercise 1

The datasaurus dozen file has 1846(142*13) rows and 3 columns. The variables included are dataset,x, and y.

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Ploting star data set
```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculating the correlation between x and y in the star dataset
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```
Correlation coefficient between x and y for the dino compared to star is -.063


### Exercise 4

Plotting circle data set

```{r}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```
Calculating the correlation between x and y in the star dataset
```{r}
circle_data %>%
  summarize(r = cor(x, y))

```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
